\subsection{Criterion}\label{subsec:criterion}

The criterion is a list of requirements for the design of the system.
It shows the fields of the system that the group has focuses on.
The specific criteria were taken from a list of standard criteria for software systems~\cite[180]{mathiassen2018}. 

\begin{table}[H]
    \centering
    \resizebox{\columnwidth}{!}{%
        \begin{tabular}{ccccc}
            \toprule
            \textbf{Criterion} & \textbf{Very important} & \textbf{Important} &
            \textbf{Less important} & \textbf{Irrelevant} \\ \midrule
            Usable & X \\ \midrule
            Secure & & X \\ \midrule
            Efficient & & & & X \\ \midrule
            Correct & X \\ \midrule
            Reliable & & X \\ \midrule
            Maintainable & & & X \\ \midrule
            Testable & & & X \\ \midrule
            Flexible & & & X \\ \midrule
            Comprehensible & & X \\ \midrule
            Reusable & & & & X \\ \midrule
            Portable & & & & X \\ \midrule
            Interoperable & & & & X \\ \bottomrule
        \end{tabular}%
    }
\end{table}

% textidote: ignore begin % complains about "important" being repeatd
The two most important criteria for the system are that it is correct and usable.
% textidote: ignore end
The system must be correct, because system must work as intended.
That means that the group has to fulfil all the requirements that they have set for the system.
The system must also be usable, because the system is intended for café workers, that may not have experience with
analytical systems before.
% textidote: ignore begin
Security, reliability, and comprehensibility are also important to the system.
% textidote: ignore end
Since the system is dealing with sensitive sales data, it is vital that the system is secure.
It needs to be reliable, because the system is intended to be used in a business setting, where the system must be 
available when needed.
Comprehensibility is needed for the same reason as usability.

% textidote: ignore begin
Maintainability, testability, and flexibility are less important, because they are not directly related to the
functionality of the system.
% textidote: ignore end
The group did make sure to keep these criteria in mind when designing the system.

The system is not efficient, because the group is not looking to profit from the system.
Reusability, portability, and interoperability are also irrelevant, because the system is not designed to be used by
other businesses.
However, if another business is using the same~\acrshort{epos} system as Nova café is using, the system should in
theory work with that business.
