\pagebreak
% textidote: ignore begin
\section{Conclusion}\label{sec:conclusion}
To get a better understanding of the problem see~\ref{subsec:the-current-situation} and~\ref{subsec:problem-statement}.
We started out by having an interview with the owners of Nova to get a better understanding of the problem.
When we had a better understanding of the problem, we came to the problem statement.
% textidote: ignore end

\textit{How can we design an application that provides the café owners with a comprehensive overview of their sales and
facilitates better decision-making based on the available data, while ensuring that the system is intuitive and
accessible for all users?}

% textidote: ignore begin
The way we came to this formulation of the problem statement was mainly through the interview with the owners of Nova.
They told us about the problems they were having with their current system and what they would like to see in a
new system.
% textidote: ignore end

The solution was developed using the knowledge we gained from the OOP course where we learned about Spring Boot and
different design patterns.
We already had some experience prior with databases like SQL, and so we decided to use PostgreSQL for the database.
We also managed to cover some of our models with unit tests not covering a 100\% of the code but a good amount.
Furthermore, the group also evaluated the system's user interface as well as the system as a whole to make sure that it
was working as intended.

The final product was a system that could be used by the café owners to get a better overview of their sales and
facilitate better decision-making based on the available data.
The features of the system were based on the requirements that the owners of Nova had given us.
That includes the ability to see the sales of the café, the ability to see the sales of the individual products, and the
ability to see when those products were sold hourly.
The data is presented mainly in two different ways, a table and a graph, and the table is a heatmap that shows the sales
of the products hourly.

It is the group's assessment that the system is working as intended
and that it is a good solution to the problem that the owners of Nova had.
% textidote: ignore begin
We feel the core of the problem has been solved even through we are aware that there are some improvements that could
be made to the system as mentioned in the discussion Section~\ref{sec:discussion-conclusion}.
% textidote: ignore end
