% textidote: ignore begin
\subsection{Back-End Libraries}\label{subsec:back-end-libraries}
% textidote: ignore end

In the back end several libraries and external code and services is used to enable and leverage the functionality of the
application.
Some of the most important ones are mentioned in this section.

\subsubsection{Amazon Cognito}

For user sign-in and access control, Amazon Cognito~\cite{cognito2024} is used.
Amazon Cognito provides quality of life features for the sign-up and sign-in process of users.
By using this service, the need to implement a sign-up and sign-in logic is eliminated while enabling the group to focus
on the core mechanics of the application.
Amazon Cognito seamlessly provides secure access to the website and furthermore enables 2-factor-authentication.
Users and admins can be added in their interface and will then be able to access the NOVA Dashboard.
Importantly, as the application is tailored for NOVA specifically, the full access to the Cognito dashboard can be
granted to the owners of NOVA without issue and further customization.

% textidote: ignore begin
\subsubsection{Spring Boot dependencies}
% textidote: ignore end

Lastly, some interesting Spring Boot dependencies used in the back-end application are mentioned.
These include:

\begin{itemize}
    \item \textbf{MapStruct:}
    This dependency, also called~\url{org.mapstruct:mapstruct}, allows for easier mapping between DTOs and
    entity models.
    In short, it simplifies complex mapping logic.

    \item \textbf{Batch Processing:}
    This dependency, also called~\texttt{spring-boot-starter-batch}, provides an abstraction for batch processing.

    \item \textbf{Spring Boot Starters:}
    Several starters are used.
    One of these is the~\texttt{spring-boot-starter-oauth2-resource-server} dependency, which is used for
    OAuth2 authentication.

    \item \textbf{CSV Validation:}
    The~\url{uk.gov.nationalarchives:csv-validator-java-api} dependency is used to validate and process CSV
    files.
\end{itemize}
