% textidote: ignore begin
\subsection{Future Development}\label{subsec:future-development}
% textidote: ignore end

In this section, we will discuss the potential future development of the system.
The system has a lot of potential for future development, as it is a very basic implementation of the idea.
All the features that could be implemented in the future will be provided in a list below, with an expanded
explanation of each feature.

\begin{itemize}
    \item API Integration
    \item Faster response time
\end{itemize}

% textidote: ignore begin
\subsubsection{API Integration}
% textidote: ignore end

The system could be more user-friendly if the system could be integrated with an API instead of uploading CSV files
to the system.
By having an API, the system would seamlessly update the data in the system, and the user would not have to upload,
making the system more automated and user-friendly.
The reason why this was not implemented is because of the~\acrshort{epos} system of the company, which does not provide
an API\@.

% textidote: ignore begin
\subsubsection{Faster response time}
% textidote: ignore end

The system could be improved by having a faster response time.
The system is currently already fast enough for the user to use, but it could always be improved.
One of our would-haves was to have a faster response time, but we did have time to prioritize optimizing the system
for speed.
One way to improve the response time could be to optimize the reading and writing of the data in the system.
We could make asynchronous calls to reading the CSV files, which would make the system faster.
