The issues Nova has been facing is described in Section~\ref{subsec:the-current-situation} and
Section~\ref{subsec:problem-statement}.
To specify the problem statement, the authors started by interviewing the owners of Nova.
Here different issues were discussed, and through this back and forth the following has been derived.

\textit{How can we design an application that provides the café owners with a comprehensive overview of their sales and
facilitates better decision-making based on the available data, while ensuring that the system is intuitive and
accessible for all users?}
% textidote: ignore begin
The way this formulation of the problem statement came to be has mainly been through the interview with the owners of
% textidote: ignore end
Nova.
Nova's owners described the difficulties they were having with their current system and what they would like to see in a
new system.

The solution was developed using the knowledge gained from the OOP course where the authors learned about Spring Boot
and different design patterns.
Although the authors already had some experience prior with databases like SQL,
and so it was decided that PostgreSQL would be used for the database.
The authors also managed to cover some models with unit tests, though not covering 100\% of the code.
Furthermore, the system's user interface as well as the system as a whole, was evaluated to make sure that it
was working as intended.

The final product was a system that could be used by the café owners to get a better overview of their sales and
facilitate better decision-making based on the available data.
The features of the system were based on the requirements that the owners of Nova had given the authors.
That includes the ability to see the sales of the café, the ability to see the sales of the individual products, and the
ability to see when those products were sold hourly.
The data is presented mainly in two different ways, a table and a graph, and the table is a heatmap that shows the sales
of the products hourly.

It is the authors' assessment that the system is working as intended
and that it is a good solution to the problem that the owners of Nova had.

The core of the problem has been solved even though that there are some improvements that could
be made to the system as mentioned in the discussion Section~\ref{sec:future-development}.

